FictionEro - Data Cleaning

### 2025-06-04 study1/analysis/1_cleaning.qmd
push
cleaning_script incomplete
script is not rendering due to the addition of the new 60 participants

# Used for feedback screen in the new BAIT implementations
mean(rowMeans(df[c("GAAIS_Positive_12", "GAAIS_Positive_17")]))
```

@@

marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "marginalmeans") |> 
  as.data.frame() |> 
  ggplot(aes(x=AI_Knowledge, y=estimate)) +
  ggdist::stat_halfeye(data=df, aes(y=BAIT_Visual), geom="slab") +
  # ggdist::stat_dots(data=df, aes(y=BAIT_Visual), side="left") +
  # geom_boxplot(data=df, aes(y=BAIT_Visual, group=AI_Knowledge)) +
  geom_point2(data=df, aes(x=AI_Knowledge-0.08, y=BAIT_Visual), alpha=0.2, position=position_jitter(width=0.06), size=2) +
  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
  theme_minimal() +
  labs(x = "AI-Knowledge", y="BAIT - Visual")
```

>>>>

# Used for feedback screen in the new BAIT implementations
mean(rowMeans(df[c("GAAIS_Positive_12", "GAAIS_Positive_17")])) * 6
```

@@

marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "means") |> 
  as.data.frame() |> 
  ggplot(aes(x=AI_Knowledge, y=estimate)) +
  ggdist::stat_halfeye(data=df, aes(y=BAIT_Visual), geom="slab") +
  # ggdist::stat_dots(data=df, aes(y=BAIT_Visual), side="left") +
  # geom_boxplot(data=df, aes(y=BAIT_Visual, group=AI_Knowledge)) +
  geom_point2(data=df, aes(x=AI_Knowledge-0.08, y=BAIT_Visual), alpha=0.2, position=position_jitter(width=0.06), size=2) +
  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
  theme_minimal() +
  labs(x = "AI-Knowledge", y="BAIT - Visual")
```
